?????????????????

### 2022-12-02 article_1/Methodology.tex
Add random function with seeds and change variable names
Change results (tables and figures) and update apsg library
Add stereograms mean directions and remove methodology figure

@@

\noindent{The SMM can also be considered as a form of aeromagnetic survey, carried out at microscales on sources of flat topography, with high spatial resolution and greater sensitivity to magnetic moment \citep{Lima2013}. An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface \citep{Fu2020} capable of detecting the magnetic signals of SD magnetite particles (\cref{fig:QDM}). Another promising type of magnetic microscope is the magnetic tunnel junction (MTJ) with a spatial resolution greater than 7 µm, a magnetic moment sensitivity of up to 10$^{-14}$ Am$^2$ and sample-sensor distance of 7 µm. Its advantages reside in the fact that these MTJ devices do not require high bias current to operate (few tens of µA), which avoids induced magnetization signals created by artificial magnetic field during the measurements \citep{Lima2014}.}

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{QDM.png}
\caption{Sample classes accessible to QDM, SQUID microscope and 2G Enterprises SRM. The accessible region for the QDM was calculated assuming a magnetic field noise threshold of 5 nT and a minimum sensor-sample distance of 5 μm. The calculation for the SQUID microscope assumed field noise values of 15 pT and sensor-sample distance of 150 μm. Source: \cite{Fu2020}.}
\label{fig:QDM}
\end{figure}

@@

\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources. The structural index is the only necessary a priori knowledge. Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}

@@

>>>>

\begin{singlespace}

@@

\noindent{The SMM can also be considered as a form of aeromagnetic survey, carried out at microscales on sources of flat topography, with high spatial resolution and greater sensitivity to magnetic moment \citep{Lima2013}. An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface capable of detecting the magnetic signals of SD magnetite particles \citep{Fu2020}. Another promising type of magnetic microscope is the magnetic tunnel junction (MTJ) with a spatial resolution greater than 7 µm, a magnetic moment sensitivity of up to 10$^{-14}$ Am$^2$ and sample-sensor distance of 7 µm. Its advantages reside in the fact that these MTJ devices do not require high bias current to operate (few tens of µA), which avoids induced magnetization signals created by artificial magnetic field during the measurements \citep{Lima2014}.}

@@

\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources. The structural index is the only necessary a priori knowledge. Once a value for n is assumed ($n = 3$ for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}

@@

\end{singlespace}
